### 2022-03-10 omicron-generation.tex
good night (Te)

\begin{align}
\mathbb E[\tau_{g}] &= \int_0^\infty \int_0^\infty x_g f_{G|I}(x_g|x_{i,1}) b_I(x_{i,1}) \dd x_g x_{i, 1}\\
&= \frac{\int_0^\infty \int_0^\infty x_g \exp(-rx_{i,1})  f_{G|I}(x_g|x_{i,1}) f_I(x_{i,1}) \dd x_g x_{i, 1}}{\int_0^\infty  \exp(-r x) f_I(x) \dx}
\end{align}
On the other hand, the mean forward generation interval of our interest does not depend on the exponential growth rate:
\begin{equation}
\mathbb E[\hat{\tau}_{g}] = \int_0^\infty \int_0^\infty x_g f_{G|I}(x_g|x_{i,1}) f_I(x_{i,1}) \dd x_g x_{i, 1}.\\
\label{eq:meangen}
\end{equation}
Therefore, while we generally expect the mean forward generation interval to be shorter than the mean forward serial interval for a growing epidemic, correlation between symptom onset and transmissibility can also have opposite effects.

Here, we model forward incubation-period $f_I(\tau)$ and generation-interval $f_G(\tau)$ distributions with lognormal distributions.
Both distributions are parameterized by log means, $\mu_I$ and $\mu_G$, and log variances, $\sigma_I^2$ and $\sigma_G^2$.
Then, given the correlation coefficient $\rho$, the forward generation-interval distribution conditional conditional on the incubation period $f_{G|I}(\tau|\tau_{i,1})$ has a mean of $\mu_G + \sigma_G \rho (\log(\tau_{i, 1}) - \mu_I)/\sigma_I$ and a log variance of $\sigma_G^2 (1 - \rho^2)$.
Assuming that the incidence of infection is changing exponentially at rate $r$, the forward serial-interval distribution $f_S(\tau)$ for a cohort of infectors who developed symptoms at time $t = 0$ can be calculated by integrating across infection time of the infector $\alpha_1 < 0$ and of the infectee $\alpha_2 > \alpha_1$ \citep{park2021forward}:
\begin{equation}
f_S(\tau) = \frac{1}{\phi} \int_{-\infty}^0\int_{\alpha_1}^\tau \exp(r \alpha_1) f_{G|I}(\alpha_2 - \alpha_1|- \alpha_1) f_I(- \alpha_1) f_I(\tau - \alpha_2) \dd \alpha_2 \dd \alpha_1,
\label{eq:forwardserial}
\end{equation}
where $\phi$ represents the normalization constant to satisfy $\int f_S(x) \dx = 1$;
$-\alpha_1$ corresponds to the incubation period of the infector;
$\alpha_2 - \alpha_1$ corresponds to the generation interval;
and $\tau - \alpha_2$ corresponds to the incubation period of the infectee.

>>>>

\begin{align}
\mathbb E[\tau_{g}] &= \int_0^\infty \int_0^\infty x_g f_{G|I}(x_g|x_{i,1}) b_I(x_{i,1}) \dd x_g x_{i, 1}\\
&= \frac{\int_0^\infty \int_0^\infty x_g \exp(-rx_{i,1})  f_{G|I}(x_g|x_{i,1}) f_I(x_{i,1}) \dd x_g x_{i, 1}}{\int_0^\infty  \exp(-r x) f_I(x) \dx}
\end{align}

\jd{What's going on here? I'm having trouble wading through the equations, but I guess the idea is that $\tau_g$ is the mean generation interval for a symptom-based cohort, and that what we want is the mean for an infection-based cohort. Can we say that more clearly? Can we also work on accompanying notation? In particular, I don't like giving the weird one the more-normal name.}
On the other hand, the mean forward generation interval of our interest \jd{“of our interest” requires some explanation, and maybe some thought} does not depend on the exponential growth rate:
\begin{equation}
\mathbb E[\hat{\tau}_{g}] = \int_0^\infty \int_0^\infty x_g f_{G|I}(x_g|x_{i,1}) f_I(x_{i,1}) \dd x_g x_{i, 1}.\\
\label{eq:meangen}
\end{equation}
Therefore, while we generally expect the mean forward generation interval to be shorter than the mean forward serial interval for a growing epidemic, correlation between symptom onset and transmissibility can also have opposite effects.
\jd{I'm not quite following here. Can we disentangle the two effects a bit better?}

\jd{Didn't we just finish modeling incubation periods with both Weibull and lognormal? Is there a simpler way?}
Here, we model forward incubation-period $f_I(\tau)$ and generation-interval $f_G(\tau)$ distributions with lognormal distributions.
Both distributions are parameterized by log means, $\mu_I$ and $\mu_G$, and log variances, $\sigma_I^2$ and $\sigma_G^2$.
Then, given the correlation coefficient $\rho$, the forward generation-interval distribution conditional conditional on the incubation period $f_{G|I}(\tau|\tau_{i,1})$ has a mean of $\mu_G + \sigma_G \rho (\log(\tau_{i, 1}) - \mu_I)/\sigma_I$ and a log variance of $\sigma_G^2 (1 - \rho^2)$.
Assuming that the incidence of infection is changing exponentially at rate $r$, the forward serial-interval distribution $f_S(\tau)$ for a cohort of infectors who developed symptoms at time $t = 0$ can be calculated by integrating across infection time of the infector $\alpha_1 < 0$ and of the infectee $\alpha_2 > \alpha_1$ \citep{park2021forward}:
\begin{equation}
f_S(\tau) = \frac{1}{\phi} \int_{-\infty}^0\int_{\alpha_1}^\tau \exp(r \alpha_1) f_{G|I}(\alpha_2 - \alpha_1|- \alpha_1) f_I(- \alpha_1) f_I(\tau - \alpha_2) \dd \alpha_2 \dd \alpha_1,
\label{eq:forwardserial}
\end{equation}
where $\phi$ represents the normalization constant to satisfy $\int f_S(x) \dx = 1$;
$-\alpha_1$ corresponds to the incubation period of the infector;
$\alpha_2 - \alpha_1$ corresponds to the generation interval;
and $\tau - \alpha_2$ corresponds to the incubation period of the infectee.
